Type Refinements for the Working Class

### 2016-01-01 paper.tex
extend remark on behavioral character of the independence modality (#13)

\begin{remark}
  Note that we could not have simply used
  $\RMemEq{\Upsilon'\setminus\rho(a)}{M}{N}{\phi}$ as the premise in our
  definition, since that would be outside the range of significance of this
  form of judgment (i.e.\ the presuppositions fail to be satisfied); in
  particular, it is not guaranteed that the refinement $\phi$ is defined at
  $\Upsilon'\setminus\rho(a)$, and nor do we have
  $\Member{M,N}{\Exprs_\tau(\Upsilon'\setminus\rho(a))}$.
\end{remark}

>>>>

\begin{remark}
  Note that we could not have simply used
  $\RMemEq{\Upsilon'\setminus\rho(a)}{M}{N}{\phi}$ as the premise in our
  definition, since that would be outside the range of significance of this
  form of judgment (i.e.\ the presuppositions fail to be satisfied); in
  particular, it is not guaranteed that the refinement $\phi$ is defined at
  $\Upsilon'\setminus\rho(a)$, and nor do we have
  $\Member{M,N}{\Exprs_\tau(\Upsilon'\setminus\rho(a))}$.

  In fact, far from being a technical nuisance, the definition that is forced
  by the nature of our presuppositions is completely desirable, since it
  expresses a \emph{behavioral} notion of independence rather than a
  \emph{structural} one. Moreover, under the structural definition, even if
  $\phi$ is a type, $\phi\setminus a$ might fail to be a type in case there is
  a member of $\phi$ that uses $a$ which is merely computationally equivalent
  to another member that is independent of $a$.
\end{remark}
